\documentclass[11pt]{article}

\usepackage{verbatim}
\usepackage{indentfirst}
\usepackage{algorithm2e}
\usepackage{amsmath, amsthm, graphicx, caption}
\usepackage[margin=1in]{geometry}
\newtheorem{theorem}{Theorem}
\numberwithin{theorem}{subsection}
%\newtheorem{algorithm}[theorem]{Algorithm}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{definition}[theorem]{Definition}
\newcommand{\optcost}{\text{Optcost}}
\title{Keys Under the Welcome Mat}
\author{Michelle Wang, Matthew Furtney, Andrew Hyer, Michael Xu}

\begin{document}
\maketitle

\section{Snapchat Flaws}

The inspiration for this project was a description of a security flaw in Snapchat, published on the internet.\cite{1}

Snapchat encrypts images that the owner of the device it's running on is not supposed to be able to access.  Unfortunately,
it encrypts them using the hard-coded encryption key ``M02cnQ51Ji97vwT4''.  Once this key is found and known, you can use it
to decrypt these images, accessing images you're not meant to be able to see.

\section{Bulk Analysis}

% Assumes a description of the SnapChat vulnerability
  Inspired by Snapchat's snafu, we strove to find similar errors in other popular apps. We downloaded
$917$ popular Android applications in .apk form for analysis. We summarize our method and results below.

\subsection{Previous Work}

  As one may expect, we were not the first to analyze android apks for security vulnerabilities.
Cryptolint was a system designed by researchers at CMU and UCSB to analyze android apps for security vulnerabilities. 
Cryptolint uses software called Androguard for sophisticated static analysis of the decompiled Android apks.
It checks for six specific types of vulnerabilities: 

\begin{enumerate}
  \item ECB mode of block cipher operation
  \item Constant initialization vectors
  \item Constant encryption keys
  \item Static salts for Password-Based Encryption
  \item Fewer than 1000 iterations of Password-Based Encryption
  \item Constant seeds for SecureRandom()
\end{enumerate}

Unfortunately, we could not locate any source for Cryptolint. Cryptolint's site allows for submission of
applications to be analyzed, but the analyzer did not return any results for us.  The source code of their
system is not available, so we cannot use it for ourselves.   Moreover, the site only supplies $5$ analyzed apps, 
none of them very prominent or popular. Therefore, we feel justified in designing and coding our own analyzer.

\subsection{Implementation}

  Decompiling the Android applications was done with the open source tool: apktool. This program takes
an apk as input and unpacks the application in a directory, including source in Smali, 
a language used by Android's Dalvik virtual machine.
We decompiled all $917$ on a single quad-core machine. In addition to the Smali code, this process generated extraneous files
such as images, sound or fonts. 
  Our next step was to scan the directory and filter the source for relevant strings. We used the \textit{egrep} to search
each directory for lines in Smali files containing ``const-string''. We fed these lines into a Python script
which checked validity based on Shannon entropy, length, and composition (letters and numbers). Before filtering a
decompiled application averaged $200,000$ lines of Smali code. After filtering, we obtained on average only a few dozen
possible hits.
\subsection{Initial Results}

  We focused on searching for \textit{const-string} objects, or hardcoded strings, in the decompiled Smali.
At first, we focused on searching for purely high-entropy constant strings of significant length. 
After examining the initial analysis data, we noticed that a large number of cryptographic terms other than keys were being
listed. For example, ``SHA1withRSA'' was a common term that qualified as ``high-entropy''. In light of this discovery,
we decided to investigate references to cryptographic algorithms; while seeing that an app contains the string ``SHA1withRSA''
does not uncover any actual security flaws, it does tell you something about what encryption system the app uses.

\subsection{Aggregate Information}

  Investigating the frequency of cryptographic algorithms yielded some interesting results. We can use
files with a high number of references to pinpoint security hotspots in an application. Additionally, 
cryptographic libraries leave an easily recognizable pattern of crypto references. A quick scan
of our analyzed data reveals that $16$ or $17$ applications make us of the BouncyCastle/SpongyCastle crypto
libraries. The insight here is that we can easily identify which files contains crypto code and check
for hardcoded keys and other vulnerabilities in close proximity.

  Later, we shifted to searching for specific calls to symmetric block cipher methods. We 

\subsection{Back to Snapchat?}

When we ran our basic Python analyzer on Snapchat, we got some interesting results: see Figure 1 (\#TODO).

The key ``M02cnQ51Ji97vwT4'' is, as we would hope, visible here.  However, there are several other sets of
hardcoded strings that look like they could also be keys!  We looked into these, and found some interesting stuff.

There were six keys in the output that looked like they might merit attention:

\begin{itemize}
\item Two strings that look like random keys, in a file called ``RequestAuthorization''. 
\begin{itemize}
\item "iEk21fuwZApXlz93750dmW22pw389dPwOk"
\item "m198sOkJEn37DjqZ32lpRu76xmw288xSQ9"
\end{itemize}
\item Four strings that look like poorly generated passwords, in a file called ``NotificationReciever''.
\begin{itemize}
\item "2peacheszxcsnapchat88whdsb3243"
\item "2ballfacechillahzx8vhf8hh83243"
\item "2baaawnburb1f3dndddhh83243"
\item "2c00l4sk00l88vhfwkipqoewm83243"
\end{itemize}
\end{itemize}

We first Googled these strings to see if they were known of.  The first two keys were: they represent \textbf{another} security
flaw in Snapchat, by which you can access the phone numbers of all Snapchat users and create arbitrary numbers of 'dummy' users.\cite{2}

The four strings that looked like poorly done passwords, however, were not found anywhere on the Internet.  We investigated the file
they came from to see if there was anything interesting in there: see Figure 2(\#TODO)

The code here is in Smali, which is difficult to read, but what's going on on this page is simple enough.  Four integer fields (designated by
letters ``a'' through ``d'' in the decompiled code) are initialized at the top.  Each of the four strings we found is hashed into an int, which 
is inserted into one of those fields.

This means that those integer fields are functionally hard-coded themselves; while their values are recalculated every time, they're recalculated in a
deterministic way from hardcoded inputs, and so will always be the same.

\subsection{Continued Investigation}

\subsection{Potential Applications}

We think there are a lot of potential future applications to the idea of making users aware of the security (or lack thereof) of apps they use.  We
cannot think of a better example of this than that presented by Snapchat; Snapchat currently has millions of users, who are using it under the
mistaken impression that it provides security.  Given that there are two separate critical security flaws in Snapchat avaiable online (and given that
each of them has been online for months or more, with no response from Snapchat), and given our own findings, we think that Snapchat's users are being
rather badly misled by Snapchat's claims of 'security'.

\begin{thebibliography}{9}

        \bibitem{1}
        http://security.stackexchange.com/questions/52584/why-can-we-still-crack-snapchat-photos-in-12-lines-of-ruby
        \bibitem{2}
        http://gibsonsec.org/snapchat/snapchat_gibsonsec.txt

\end{thebibliography}
\end{document}
